---
title: "Practical Machine Learning Project"
author: "Srividya Bobji"
date: "Sunday, February 22, 2015"
output: html_document
---


# Executive Summary
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. 

In this project we will use data from accelerometers placed on the belt, forearm, arm, and dumbell of six participants to predict how well they were doing the exercise in terms of the classification in the data. 


# Data
We are using data available from this source: http://groupware.les.inf.puc-rio.br/har.
The training data for this project are available here: 
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here: 
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv



#### Libraries
The following libraries were used.
```{r message=FALSE}
library(caret)
library(randomForest)
```


```{r}
set.seed(12345)
```

#### Processing data
Here we are loading the data directy and fitering NA.
```{r}
training0 <- read.csv(url("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"), na.strings=c("NA"," ",""))
```

